Distributions

### 2022-01-03 Ch2_distributions/Ch2_Figures.Rmd
Change visualization of tables.

BIC_table %>% 
  mutate(dist = ifelse(dist == "lnorm", "lognormal", dist),
         dist = str_to_title(dist)) %>% 
  mutate(model = factor(model, levels = c("CP", "PP", "NP"))) %>% 
  arrange(., model) -> BIC_table
# BIC_table

@@

>>>>

BIC_table %>% 
  mutate(dist = ifelse(dist == "lnorm", "lognormal", dist),
         dist = str_to_title(dist)) %>% 
  mutate(model = factor(model, levels = c("CP", "PP", "NP"))) %>% 
  arrange(., model) -> BIC_table

BIC_table

@@

```{r eval=FALSE}
